---
title: "Intro To R Activity"
author: "Hieu Hoang"
date: "2/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. multiply 4 by 7
4 * 9

2. raise 6 to the power of 3
6 ^ 3

3. Subtract 1.5 from 10 and then raise the answer to the power of 1.3 plus 1.789
(10-1.5)^(1.3+1.789)

4. Divide 5 by 2.5 then divide the answer by 4
(5/2.5)/4

5. Create an object called “obj1” which is the number 15
obj1 <- 15
obj1

6. Create an object called “obj2”" which is the answer to the sum of 100 + 25
obj2 <- 100 + 25
obj2

7. Multiply “obj1” and “obj2” together and store the answer as another object called “obj3”
obj3 <- obj1 * obj2
obj3

8. Subtract 1 from “obj3” and calculate the 4th root (raise to power of 1/4). Save this as an object called “final.answer”
final.answer <- (obj3-1) ^ (1/4)


9. Highlight and run “final.answer” to print your answer to the console
final.answer

10. Create a vector called “my.text”" which contains two elements, the phrases “Learning R” and “is fun!”. Highlight and run the my.text variable so it prints to your console.
my.text <-c ('Learning R', 'is fun!')
my.text

11. If you haven’t already done so, save the RMarkdown file to your class folder and give it the name “RIntroDay1.rmd” or something similar.


12. Turn in this file to Blackboard. 
```{r}

```
